Problem statement and suggested project outline

### 2011-11-14 background/phd-description1.tex
Section titles, empirical evaluation
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@33 43ef1190-90fd-4dd7-a769-d0121f02b80e

While the basic feature set of the proposed standard can enable users
to create federated queries, it is not of great use as it requires
extensive prior knowledge of both the data to be queried and
performance characteristics of the involved query engines.

@@

@@

>>>>

While the basic feature set of the proposed standard can enable users
to create federated queries, it is not of great use as it requires
extensive prior knowledge of both the data to be queried and
performance characteristics of the involved query engines. Without
this knowledge, the overall performance is insufficient for any
practical applications.

@@

\section*{Paper 1: Conditional selectivity estimation on a single database}

@@

\section*{Paper 2: Empirical evaluation of implementations}

Since the main objective of the proposed work is to create systems
that have sufficient performance for practical applications, it is of
paramount importance to have methodology that can falsify any
conjecture about an implementation's performance.

In a federated regime, any query is likely to execute queries on
several different SPARQL implementations. Many of those are free
software so the algorithms they use could in principle be analyzed,
but in practice, this would be very time-consuming. Some may be
undocumented or even trade secrets, thus precluding any such
analysis. It is therefore my intention to treat the individual SPARQL
implementations as ``black boxes'' and exclusively evaluate the
performance characteristics by empirical means, aka ``benchmarking''.
